Scalar Parametrization for Joint Time-Frequency interpolation in a MIMO-OFDM channel

### 2019-10-04 paper/main.tex
Minor addition

% no need to write the numbers in your introduction. You start by explaining what is happenning currently and then propose your solution.
MIMO channels can perform significantly better if the transmitter has complete knowledge of the Channel State Information (CSIT). In a frequency-selective OFDM channel, a flat fading MIMO channel approximated each subcarrier. With the CSI information available at the transmitter, beamforming is used to increase the capacity and reduce the BER \cite{love2008overview}. The receiver has the channel knowledge, and it could provide feedback to the transmitter after quantizing it. However, it is unrealistic to feedback complete information to the transmitter, and therefore information is communicated through a limited feedback channel. 
In recent years, codebook design over the Stiefel Manifold \cite{6891198} has been proposed where the manifold structure of the channel matrix is used for its predictive quantization and interpolation across time and frequency. Another such variation of \cite{6891198} has exploited both time and frequency domain together in Stiefel Manifold \cite{Gupt1905:Predictive}. All these methods are useful, but they do so over Manifolds which has problems of getting stuck in local Maxima. Also, there are different challenged which are faced while interpolating in a high dimensional space.

>>>>

% no need to write the numbers in your introduction. You start by explaining what is happenning currently and then propose your solution.
The use of multiple antennas at the transmitter and receiver can significantly enhance the performance of wireless systems. Moreover, in these multiple-input multiple-output (MIMO) wireless systems, the transmitter can perform an better resource allocation if channel state information (CSI) is made available at the transmitter, both to improve data rates and reduce BER~\cite{love2008overview}. To this end, feeding back the channel state information from the receiver to the transmitter efficiently is necessary. In the many wireless systems that use orthogonal frequency division multiplexing (OFDM), the feedback needs to be provided to the transmitter across the many subcarriers of the system, which places a large feedback demand. However, since the channel state information varies gradually in both time and frequency, effective techniques to reduce feedback overheads exist, using frequency interpolation temporal prediction. In this paper, we focus on the problem of tracking the precoders of a MIMO-OFDM system across time and frequency for efficient CSI feedback.

In recent years, codebook design over the Stiefel Manifold \cite{6891198} has been proposed where the manifold structure of the channel matrix is used for its predictive quantization and interpolation across time and frequency. Another such variation of \cite{6891198} has exploited both time and frequency domain together in Stiefel Manifold \cite{Gupt1905:Predictive}. All these methods are useful, but they do so over Manifolds which has problems of getting stuck in local Maxima. Also, there are different challenged which are faced while interpolating in a high dimensional space.
